Article title

### 2019-07-11 NAR_DRAFT.tex
check in aml figure
add minor caption
getting much closer

\begin{figure}[t]
\begin{center}
\includegraphics{figures/wes_left_plot.pdf}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/kl_figure.png}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics{figures/aml_plot.pdf}
\end{center}
\caption{Performance on aml 31.}
\label{NAR-fig1}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{figures/fig1.pdf}
\end{center}
\caption{Model performance on 500X simulated whole exome.
\textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
A perfectly calibrated model would generate the diagonal line.
}
\label{NAR-fig2}
\end{figure*}
